### 2020-04-29 Paper/paper.tex
fixed key terms on paper
final paper changes and renamed paper pdf

\begin{abstract}
Information that best describes galaxy mergers is sparse.  Complications arise when forming postulations due to missing information such as orbital mass-ratios, orbital velocities, and orientations.  To remedy this, we devised two neural networks to analyze images and human scores from Galaxy Zoo: Mergers in the hopes that a well-fitting model - one that can find true dynamic parameters for galaxy collisions.  In the single layer neural network, the information is parsed to inform the convolution net about hyperparameters such as batch or epoch sizes.  The convolution model is designed to assign a fitness score to an input galaxy image.  That score represents an approximation of how well the image fits into predicted galaxy collision simulations.  Through the limited scope of this project there are points of interest.  Both networks achieved successful validation while eventually overfitting.  The convolution net managed with good accuracy to predict scores of mergers when compared to human grading and, perhaps, more accurate than the human scores. Though the data set we used is small and unevenly distributed, there are hopeful interpretations of the results.  Better and more data sets along with more network layers may yield better results in the future.  With more tuning, our neural networks may eliminate the need for further human rankings
\end{abstract}

@@

\begin{IEEEkeywords}
convolutional neural networks, single layer neural networks, CNN, regression model, galaxy collisions, image scoring
\end{IEEEkeywords}

@@

The galactic models and their associated human fitness
score are what were used in this project. The human fitness
scores were directly applied, while the galactic models had to
be visualized again. The galactic models were sent through
SPAM again with a larger number of particles to obtain a 
higher resolution image of the colliding galaxies. These model
images and the human fitness scores are used \cite{WallinJSPAM}\cite{WallinGalaxyZoo}.

@@

Fig. \ref{fig:convWeight1} and Fig. \ref{fig:convWeight2} show the weights for the first and second convolution layers respectively. However, it is hard to glean and useful information from just these weights on their own. That is why we have shown the activations of units in the first layer in Fig. \ref{fig:layer1activations}. We can see that for this specific activation, the net was processing a model that was very similar to the target image. We can see units that are picking up the major features: galactic cores, tidal distortions, and the bridge. We can also plainly see the units that are detecting the edges of the galaxies, as well as some units that aren't really being utilized.

>>>>

\begin{abstract}
Information that best describes galaxy mergers is sparse.  Complications arise when forming postulations due to missing information such as orbital mass-ratios, orbital velocities, and orientations.  To remedy this, we devised two neural networks to analyze images and human scores from Galaxy Zoo: Mergers in the hopes of finding a well-fitting model, one that can find true dynamic parameters for galaxy collisions.  In the single layer neural network, the information is parsed to inform the convolution net about hyperparameters such as batch or epoch sizes.  The convolution model is designed to assign a fitness score to an input galaxy image.  That score represents an approximation of how well the image fits into predicted galaxy collision simulations.  Through the limited scope of this project there are points of interest.  Both networks achieved successful validation while eventually overfitting.  The convolution net managed with good accuracy to predict scores of mergers when compared to human grading and, perhaps, more accurate than the human scores. Though the data set we used is small and unevenly distributed, there are hopeful interpretations of the results.  Better and more data sets along with more network layers may yield better results in the future.  With more tuning, our neural networks may eliminate the need for further human rankings
\end{abstract}

@@

\begin{IEEEkeywords}
convolutional neural networks, single layer neural networks, CNN, galaxy collisions, image scoring
\end{IEEEkeywords}

@@

The galactic models and their associated human fitness
scores are what were used in this project. The human fitness
scores were directly applied, while the galactic models had to
be visualized again. The galactic models were sent through
SPAM again with a larger number of particles to obtain a 
higher resolution image of the colliding galaxies. These model
images and the human fitness scores are used \cite{WallinJSPAM}\cite{WallinGalaxyZoo}.

@@

Fig. \ref{fig:convWeight1} and Fig. \ref{fig:convWeight2} show the weights for the first and second convolution layers respectively. However, it is hard to glean any useful information from just these weights on their own. That is why we have shown the activations of units in the first layer in Fig. \ref{fig:layer1activations}. We can see that for this specific activation, the net was processing a model that was very similar to the target image. We can see units that are picking up the major features: galactic cores, tidal distortions, and the bridge. We can also plainly see the units that are detecting the edges of the galaxies, as well as some units that aren't really being utilized.
